### 2013-11-11 research/paper/figure/mstar_parkinson.tex
uploaded 2.54 11-11-2013

    \end{picture}
  \caption{Mean power as a function of damping factor. Data presented in both (a) and (b) were calculated using input data at \reynoldsnumber=22300 \cite{Parkinson1964} where (a) shows mean power data at six different mass ratios: $m^*=1164$ (\ding{83}), $m^*=100$ (\ding{116}), $m^*=50$ (\ding{108}), $m^*=10$ (+), $m^*=5$ (\ding{110}) and $m^*=1$ ($\times)$ at \ustar=175. Data presented in (b) shows mean power data at three different reduced velocities: \ustar=75 (\ding{108}), \ustar=175 (\ding{83}) and \ustar=375 (\ding{116}) and \ustar=375 (\ding{83}) at $m^*=10$. The maximum mean power tend to increase with decreasing $m^*$ as well as increasing \ustar at low $m^*$.}

>>>>

    \end{picture}
  \caption{Mean power as a function of damping factor. Data presented in both (a) and (b) were calculated using input data at \reynoldsnumber=22300 \cite{Parkinson1964} where (a) shows mean power data at six different mass ratios: $m^*=1164$ (\ding{83}), $m^*=100$ (\ding{116}), $m^*=50$ (\ding{108}), $m^*=10$ (+), $m^*=5$ (\ding{110}) and $m^*=1$ ($\times)$ at \ustar=175. Data presented in (b) shows mean power data at three different reduced velocities: \ustar=75 (\ding{108}), \ustar=175 (\ding{116}) and \ustar=375 (\ding{83}) at $m^*=10$. The maximum mean power tend to increase with decreasing $m^*$ as well as increasing \ustar at low $m^*$.}

### 2013-11-11 research/paper/figure/time_history_msar_mass.tex
uploaded 2.54 11-11-2013

  \caption{ Time histories of displacement and velocity at \reynoldsnumber=22300, \ustar=175 and $\frac{c}{\rho\mathcal{A}U}=9.3\times10^{-1}$. The velocity time histories are presented for: (a) $m^*=1164$; (b) $m^*=10$; (c) $m^*=5$. The time history of displacement are presented for: (a) $m^*=1164$; (b) $m^*=10$; (c) $m^*=5$   As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal and the displacement signal tend to move towards a triangular signal due to reduction in inertia.}

>>>>

  \caption{ Time histories of displacement and velocity at \reynoldsnumber=22300, \ustar=175 and $\frac{c}{\rho\mathcal{A}U}=9.3\times10^{-1}$. The velocity time histories are presented for: (a) $m^*=1164$; (b) $m^*=10$; (c) $m^*=5$. The time histories of displacement are presented for: (a) $m^*=1164$; (b) $m^*=10$; (c) $m^*=5$   As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal and the displacement signal tend to move towards a triangular signal due to reduction in inertia.}

### 2013-11-11 research/paper/figure/time_history_msar_ustar.tex
uploaded 10.23 November 8th
uploaded 2.54 11-11-2013

  \caption{Time histories of velocity. Data presented at \reynoldsnumber=22300, $m^*=10$ and $\frac{c}{\rho\mathcal{A}U}=9.3\times10^{-1}$ at three different reduced velocities: (a) $\ustar=75$, (b) $\ustar=175$ and (a) $\ustar=375$. As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal due to the reduction in inertia.}

  \label{time_history_mstar}
\end{figure}

>>>>

  \caption{  Time histories of displacement and velocity at \reynoldsnumber=22300, $m^*=10$ and $\frac{c}{\rho\mathcal{A}U}=9.3\times10^{-1}$. The velocity time histories are presented for: (a) \ustar=75; (b) \ustar=175 (c) \ustar=375. The time histories of displacement are presented for: (a) \ustar=75; (b) \ustar=175; (c) \ustar=375.   As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal and the displacement signal tend to move towards a triangular signal.}

  \label{time_history_mstar_ustar}
\end{figure}
